---
title: "4-Nov-2024"
author: "Margaret Dougher"
format: html
editor: visual
---

## Setting things up 
```{r}
rm(list=ls()) #clear R's brain
library(here)
library(tidyverse)
library(ggfortify)
```

## Importing Data
```{r}
trees <- read.csv(here("Data", "Forest_Tree_DBH_F21.csv"))
glimpse(trees)
trees$Forest <- as.factor(trees$Forest)
```

## Plotting and examining the data
```{r}
ggplot(trees, aes(x = Forest, y = DBH_cm)) +
  geom_boxplot() +
  theme_bw() +
  coord_flip()
```

## Constructing the ANOVA test
```{r}
model_trees <- lm(DBH_cm ~ Forest, data = trees)
```

## Checking assumptions
```{r}
autoplot(model_trees, smooth.colour = NA)
```

## Making an inference from a one-way ANOVA
```{r}
anova(model_trees)
```

## Using treatment contrasts
```{r}
summary(model_trees)
```

```{r}
library(multcomp)
```

Let's conduct a Tukey's HSD (honestly significant differences) test.
pch1 stands for post_hoc_comp.
```{r}
phc1 <- glht(model_trees, linfct = mcp(Forest = "Tukey"))
summary(phc1)
```

We can also ask for a "compact letter display" of these results
```{r}
cld(phc1)
```
Forests that do not have the same letter are different. 

