---
title: "21 Oct 2024 - review"
format: html
editor: visual
---

Download the dataset called "birds_and_mammals.csv" from today's module and put it in your Data folder.

Set up your workspace and read in the .csv. Name it "critters"

```{r}
rm(list=ls())
library(here)
library(tidyverse)

critters <- read.csv(here("Data", "birds_and_mammals.csv"))
```

Filter just for mammals in the order Carnivora and make a new dataset called "carnivores"

```{r}
carnivors <- critters |> filter(Order == "Carnivora")
```

create a histogram of maximum longevity for carnivores.

```{r}
ggplot(carnivors, aes())
```

Now make a scatterplot comparing max_longevity_years vs. adult_wt_g

```{r}

```

Use code (rather than scrolling the data) to determine which species it is that has the highest maximum longevity?

```{r}

```

Use code to determine the two species between 2.5e+05 and 3e+05 in adult body mass.

```{r}

```

Now make a boxplot of max longevity as a function of family. Set the y-axis label to "maximum longevity, years". Make the points red and somewhat transparent.

```{r}

```
